Exploring Hillary Clinton's Emails\thanks{STATS 601 final project. All of the code used to download, process, and analyze the data for this project is available at \url{https://github.com/lbybee/601_Final_Project} and has been open-sourced under the MIT license.}

### 2016-04-21 paper/paper.tex
add model background and coherence sources

\usepackage{tikz}

@@

\section{Topic Modeling}
To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA). LDA is a popular form of topic modeling that has historically been effective for identifying meaningful ``topics'' in text corpuses.\footnote{note on estimation}

The primary parameter that we need to specify for LDA is the number of topics. Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer. In particular, we considered the UMass and UCI measures.\footnote{add bib here} However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, anywhere from 15 to 50 topics used. As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.

@@

\subsection{Multinomial Logistic Regression}
While the above results do give some sense of which senders are most associated with which topics, we next want to formalize this approach and get more general results that can more easily show us which senders are most related to each topic. To approach this problem we turn to multinomial logistic regression as a solution. Multinomial logistic regression generalizes the logistic regression approach to the case with more labels than two. Part of the output of multinomial logistic regression is a $P \times K$ matrix of coefficients corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.

>>>>

\usepackage{tikz}
\usetikzlibrary{bayesnet}

@@

\section{Topic Modeling}
To try and move beyond the limitations of spectral clustering and capture some of the content of the emails as well as structure, we next turn to latent Dirichlet allocation (LDA). LDA is a popular form of topic modeling that has historically been effective for identifying meaningful ``topics'' in text corpuses.  See Figure~\ref{fig:lda_graph} for a graphical representation of the model.  The model assumes that each document can be represented as a mixture of topics, and that each word is drawn based on the topic proportions in the corresponding document.  $\theta$ represents the topic proportion for each document and $\beta$ represents the topic weights for each word.  The model is estimated using variational Bayesian methods.

\begin{figure}
\centering
\begin{tikzpicture}[scale=1.0, every node/.style={transform shape}]
\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100]
  \node[main] (alpha) {$\alpha$};
  \node[main] (theta) [right=of alpha] {$\theta$};
  \node[main] (z) [right=of theta] {$z$};
  \node[main] (beta) [above=of z] {$\beta$};
  \node[main, fill=black!10] (w) [right=of z] {$w$};
  \edge {alpha} {theta};
  \edge {theta} {z};
  \edge {z,beta} {w};
  \plate {words} {(z)(w)} {$N_m$};
  \plate {docs} {(theta)(z)(w)(words.south east)(words.north west)} {$M$};
\end{tikzpicture}
\caption{LDA Graphical Representation}
\label{fig:lda_graph}
\end{figure}

The primary parameter that we need to specify for LDA is the number of topics. Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer. In particular, we considered the UMass and UCI measures.\footnote{David Mimno, Hanna M. Wallach, Edmund Talley, Mirian Leenders, and Andrew McCallum. Optimizing Semantic Coherence in Topic Models. 2011.}\footnote{David Newman, Jey Han Lau, Karl Grieser, and Timothy Baldwin. Automatic Evaluation of Topic Coherence. 2010.}

@@

\subsection{Multinomial Logistic Regression}
While the above results do give some sense of which senders are most associated with which topics, we next want to formalize this approach and get more general results that can more easily show us which senders are most related to each topic. To approach this problem we turn to multinomial logistic regression as a solution. Multinomial logistic regression generalizes the logistic regression approach to the case with more labels than two. The probability that the $j$th label is assigned to the $i$th email is,

\begin{equation} \label{eq:smax}
p(y_i = j | x_i, \boldsymbol{\beta}) = \frac{\exp\{\beta_j^Tx_i\}}{\sum_{1\leq k\leq K} \exp\{\beta_k^Tx_i\}}
\end{equation}

This produces a $P \times K$ matrix of coefficients, $\boldsymbol{\beta}$, corresponding to how strongly related each of the $K$ variables of interest are related to each of the $P$ labels.
